\ssp

% John Wawrzynek
I would like to thank my research advisor Prof. John Wawrzynek for his time and effort in guiding and supporting of my graduate study at University of California Berkeley. Discussions we had, academic related or non-academic related, are highlights of my graduate study and will continue to guide me afterward. \par

\vspace{0.3cm}

I would also like to thank Prof. Elad Alon for his time and feedback for this work. \par

\vspace{0.6cm}

% NSERC
Special thanks to The Natural Sciences and Engineering Research Council of Canada (NSERC) for two graduate fellowships in 2011 and 2012 respectively. \par

\vspace{0.3cm}

% Commerical Tools
I would like to thank Synopsys for their ASIC Tools and TSMC for their Standard Cell Library. \par

\vspace{0.3cm}

% Research Staff and Group
Many thanks to Shaoyi for this assistance through many discussions with him on the project. Special thanks to Mr. Brain Richard for his support in using the ASIC Tools. I would also like to acknowledge the reconfigurable computing group's members for their critiques on the work. \par

\vspace{0.6cm}

% Family
To my parents, Yuan An Liu and Gui Ju Li, I do not know words that describe your love to me. Thanks for all the spiritual and financial support throughout my life. \par

\vspace{0.3cm}

% Friend
Finally, I would thank Mr. Chu Tong for proofreading and editing my report. \par

\vspace{0.1cm}

Special thanks to CEF's brothers and sisters support in their fellowship, encouragement, prayers. \par